\text{Additive drift with tail bounds}

### 2021-10-14 article.tex
adjusted the section about sub-Gaussian

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{mathtext}
\usepackage[T1,T2A]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{a4wide}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{subcaption}

@@

\end{proof}
\subsection{Theorem for sub-gaussian processes}

\begin{theorem}
    Suppose $X_t$ has a drift of at most $\varepsilon > 0$ and $(X_t - \varepsilon t)$ is $(c, \delta)$ - sub-Gaussian. Let \(X_0\) be \(a \in \mathbb{R}\) and let \(T\) be the first moment in time when \(X_t\) exceeds some \(b > a\). Then for all \(s \leq \frac{b - a}{2\varepsilon}\) we have

    \[\Pr[T \leq s] \leq exp\left(-\frac{b - a}{4} min\left(\delta, \frac{b - a}{2cs}\right)\right)\]
\end{theorem}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{mathtext}
\usepackage[T1,T2A]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{a4wide}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{mathtools}

@@

\end{proof}
\subsection{Sub-Gaussian processes}

In~\cite{Kotzing16} the authors use the notion of sub-Gaussian processes, which are (informally speaking) the processes such that their steps are dominated by a normal distribution. More formally, a process $\{X_t\}_{t\in\N}$ is called $((c_t)_{t \in \N}, \delta)$-sub-Gaussian, iff for all $t \in \N$ and for all $\lambda \in [0, \delta]$ we have
\begin{align*}
    E\left[e^{\lambda(X_{t + 1} - X_t)} \mid X_1, \dots X_t\right] \le e^{z^2c_t/2}.
\end{align*}
If $c_t$ is equal to some $c$ for all $t \in \N$, then the process is called $(c, \delta)$-sub-Gaussian.
As it was noted in~\cite{Kotzing16}, all sub-Gaussian processes are super-martingales, that is, for all $t \in \N$ we have
\begin{align*}
    E[X_{t + 1} - X_t \mid X_1, \dots, X_t] \le 0.
\end{align*}

For such processes we have the following theorem (we slightly change the formulation in order to compare it with the negative drift approach).

\begin{theorem}[Theorem 11 in~\cite{Kotzing16}]
    Let $\{X_t\}_{t \in \N}$ be $((c_t)_{t \in \N}, \delta)$-sub-Gaussian. For all $t \in \N$ let $C_t \coloneqq \sum_{i = 1}^{t - 1} c_i$. Let $x>0$ be some constant and let $T$ be the minimum $t$ such that when $X_t \ge X_0 + x$. Then for all time bounds $B \in \N$ we have
    \begin{align*}
        \Pr\left[T \le B\right] \le \exp\left(-\frac{x}{2}\min\left\{\delta, \frac{x}{C_B}\right\}\right).
    \end{align*}
\end{theorem}

% \begin{theorem}
%     Suppose $X_t$ has a drift of at most $\varepsilon > 0$ and $(X_t - \varepsilon t)$ is $(c, \delta)$ - sub-Gaussian. Let \(X_0\) be \(a \in \mathbb{R}\) and let \(T\) be the first moment in time when \(X_t\) exceeds some \(b > a\). Then for all \(s \leq \frac{b - a}{2\varepsilon}\) we have

%     \[\Pr[T \leq s] \leq exp\left(-\frac{b - a}{4} min\left(\delta, \frac{b - a}{2cs}\right)\right)\]
% \end{theorem}
